PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity

### 2023-10-15 analysis/analysis.Rmd
put analysis in folder

df <- haven::read_sav("data/Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

@@

```{r, message=FALSE, warning=FALSE, results='asis'}
df2 <- haven::read_sav("data/Study 6 IAS.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other")))) |> 
  select(-ESL)

@@

```{r, message=FALSE, warning=FALSE}
scores <- as.data.frame(predict(cfa4h))
scores$Participant <- df3$Participant
write.csv(scores, "data/IASR_scores.csv", row.names = FALSE)
```

>>>>

df <- haven::read_sav("../data/Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

@@

```{r, message=FALSE, warning=FALSE, results='asis'}
df2 <- haven::read_sav("../data/Study 6 IAS.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other")))) |> 
  select(-ESL)

@@

```{r, message=FALSE, warning=FALSE}
scores <- as.data.frame(predict(cfa4h))
scores$Participant <- df3$Participant
write.csv(scores, "../data/IASR_scores.csv", row.names = FALSE)
```
